Manuscript

### 2018-11-01 manuscript.Rmd

```{r}
g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_v2_10_10_2018.tsv", sep = "\t", header = TRUE)
g2p$Drug <- tolower(g2p$Drug)
g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
g2p <- subset(g2p, grepl("^CID", g2p$DrugID))

>>>>

```{r}
g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_withPositions_10_23_2018.csv", sep = "\t", header = TRUE, row.names = 1)
g2p$Drug <- tolower(g2p$Drug)
g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
g2p <- subset(g2p, grepl("^CID", g2p$DrugID))
g2p[g2p == -1] <- NA
